---
title: "R Notebook"
output: html_notebook
---

# Setting up the workspace dir
```{r}
#uncomment to set current workspace
#setwd("path/to/project/repo")
```

# Import the librarires
```{r}
#Isntall the necessary libraries
library("raster")
library("EMMIXmfa")
library("aricode")
library("OpenImageR")
library("clusterCrit")
library("FactoMineR")
library("R.matlab")
library(clustrd)
```

# Some helper functions
```{r}
##TODO : this function has strange behaviour and was left for developement.

# variate = function(data,labels,n_clus,n_dims = c(2,64), alphas = c(1),rotate = FALSE){
#   resutls = list()
#   count = 1
#   for (nd in n_dims)
#   {
#     for (alpha in alphas)
#     {
#       res = c()
#       if(rotate)
#       {
#         res = cluspca(data = data,nclus = n_clus, ndim =  nd, alpha = alpha, seed = 1234,rotation = "varimax")
#         #evaluating the clustering
#         res['nmi'] = NMI(as.vector(res['cluspca']$cluster),as.vector(labels))
#         res['ari'] = ARI(as.vector(res['cluspca']$cluster),as.vector(labels))
#         
#         #evaluating the dim_reduc
#         ## Firts pca
#         pca<-PCA(data,ncp=nd,scale.unit = TRUE)
#         res['pca_eval'] = intCriteria(pca$ind$coord,as.integer(labels),c("Silhouette","Davies_Bouldin"))
#         
#         #Then the method passed in this function (for now it's global and it's cluspca)
#         res['method_eval'] = intCriteria(res['cluspca']$obscoord,as.integer(labels),c("Silhouette","Davies_Bouldin"))
#         resutls[count] = res
#         count = count +1
#       }
#       else
#       {
#         res['cluspca'] = cluspca(data = data,nclus = n_clus, ndim =  nd, alpha = alpha, seed = 1234)
#         #evaluating the clustering
#         res['nmi'] = NMI(as.vector(res['cluspca']$cluster),as.vector(labels))
#         res['ari'] = ARI(as.vector(res['cluspca']$cluster),as.vector(labels))
#         
#         #evaluating the dim_reduc
#         ## Firts pca
#         pca<-PCA(data,ncp=nd,scale.unit = TRUE)
#         res['pca_eval'] = intCriteria(pca$ind$coord,as.integer(labels),c("Silhouette","Davies_Bouldin"))
#         
#         #Then the method passed in this function (for now it's global and it's cluspca)
#         res['method_eval'] = intCriteria(res['cluspca']$obscoord,as.integer(labels),c("Silhouette","Davies_Bouldin"))
#   
#         resutls[count] = res
#         count = count +1
#       }
#     }
#   }
#   return(resutls)
# }
```

# COIL100 Dataset
## IMPORT THE DATASET
```{r}
#CHANGE THE name of the file to USPC.mat
dataset<- readMat("data/COIL100.mat")
#change $fea to poissbly X or x 
features<-dataset$fea
#change $gnd to possibly y or Y  
labels<-as.vector(dataset$gnd)
n_labels = length(unique(labels))
ndim= 2
dim(features)
```

## RUN cluspca wit different parameters
```{r}
tandem = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 1, seed = 1234,rotation = "varimax",nstart = 1)
RKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0.5, seed = 1234,rotation = "varimax")
FKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0, seed = 1234,rotation = "varimax")

#evaluating the clustering
##tandem
res.tandem.nmi = NMI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.ari = ARI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.cri = intCriteria(tandem$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.tandem.nmi
res.tandem.ari
res.tandel.cri

##RKM
res.rkm.nmi = NMI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.ari = ARI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.cri = intCriteria(rkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.rkm.nmi
res.rkm.ari
res.rkm.cri


##FKM
res.fkm.nmi = NMI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.ari = ARI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.cri = intCriteria(fkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.fkm.nmi
res.fkm.ari
res.fkm.cri

```

# COIL20
## IMPORT THE DATASET
```{r}
#CHANGE THE name of the file to USPC.mat
dataset<- readMat("data/COIL20.mat")
#change $fea to poissbly X or x 
features<-dataset$fea
#change $gnd to possibly y or Y  
labels<-as.vector(dataset$gnd)
n_labels = length(unique(labels))
ndim= 2
dim(features)
```

## RUN cluspca wit different parameters
```{r}
tandem = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 1, seed = 1234,rotation = "varimax",nstart = 1)
RKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0.5, seed = 1234,rotation = "varimax")
FKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0, seed = 1234,rotation = "varimax")

plot(tandem$ind$obscoord, col=labels)
plot(RKM$ind$obscoord, col=labels)
plot(FKM$ind$obscoord, col=labels)


#evaluating the clustering
##tandem
res.tandem.nmi = NMI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.ari = ARI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.cri = intCriteria(tandem$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.tandem.nmi
res.tandem.ari
res.tandel.cri




##RKM
res.rkm.nmi = NMI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.ari = ARI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.cri = intCriteria(rkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.rkm.nmi
res.rkm.ari
res.rkm.cri


##FKM
res.fkm.nmi = NMI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.ari = ARI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.cri = intCriteria(fkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.fkm.nmi
res.fkm.ari
res.fkm.cri

```

# MNIST 
## IMPORT THE DATASET
```{r}
#CHANGE THE name of the file to USPC.mat
dataset<- readMat("data/MNIST.mat")
#change $fea to poissbly X or x 
features<-dataset$fea
#change $gnd to possibly y or Y  
labels<-as.vector(dataset$gnd)
n_labels = length(unique(labels))
ndim= 2
dim(features)
```
## RUN cluspca wit different parameters
```{r}
tandem = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 1, seed = 1234,rotation = "varimax",nstart = 1)
RKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0.5, seed = 1234,rotation = "varimax")
FKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0, seed = 1234,rotation = "varimax")

plot(tandem$ind$obscoord, col=labels)
plot(RKM$ind$obscoord, col=labels)
plot(FKM$ind$obscoord, col=labels)



#evaluating the clustering
##tandem
res.tandem.nmi = NMI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.ari = ARI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.cri = intCriteria(tandem$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.tandem.nmi
res.tandem.ari
res.tandel.cri

##RKM
res.rkm.nmi = NMI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.ari = ARI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.cri = intCriteria(rkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.rkm.nmi
res.rkm.ari
res.rkm.cri


##FKM
res.fkm.nmi = NMI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.ari = ARI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.cri = intCriteria(fkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.fkm.nmi
res.fkm.ari
res.fkm.cri

```
# ORL
## IMPORT THE DATASET
```{r}
#CHANGE THE name of the file to USPC.mat
dataset<- readMat("data/ORL.mat")
#change $fea to poissbly X or x 
features<-dataset$X
#change $gnd to possibly y or Y  
labels<-as.vector(dataset$Y)
n_labels = length(unique(labels))
ndim= 2
dim(features)
```
## RUN cluspca wit different parameters
```{r}
tandem = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 1, seed = 1234,rotation = "varimax",nstart = 1)
RKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0.5, seed = 1234,rotation = "varimax")
FKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0, seed = 1234,rotation = "varimax")

plot(tandem$ind$obscoord, col=labels)
plot(RKM$ind$obscoord, col=labels)
plot(FKM$ind$obscoord, col=labels)



#evaluating the clustering
##tandem
res.tandem.nmi = NMI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.ari = ARI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.cri = intCriteria(tandem$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.tandem.nmi
res.tandem.ari
res.tandel.cri

##RKM
res.rkm.nmi = NMI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.ari = ARI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.cri = intCriteria(rkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.rkm.nmi
res.rkm.ari
res.rkm.cri


##FKM
res.fkm.nmi = NMI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.ari = ARI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.cri = intCriteria(fkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.fkm.nmi
res.fkm.ari
res.fkm.cri

```
# USPS
## IMPORT THE DATASET
```{r}
#CHANGE THE name of the file to USPC.mat
dataset<- readMat("data/USPS.mat")
#change $fea to poissbly X or x 
features<-dataset$X
#change $gnd to possibly y or Y  
labels<-as.vector(dataset$y)
n_labels = length(unique(labels))
ndim= 2
dim(features)
```
## RUN cluspca wit different parameters
```{r}
tandem = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 1, seed = 1234,rotation = "varimax",nstart = 1)
RKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0.5, seed = 1234,rotation = "varimax")
FKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0, seed = 1234,rotation = "varimax")

plot(tandem$ind$obscoord, col=labels)
plot(RKM$ind$obscoord, col=labels)
plot(FKM$ind$obscoord, col=labels)



#evaluating the clustering
##tandem
res.tandem.nmi = NMI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.ari = ARI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.cri = intCriteria(tandem$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.tandem.nmi
res.tandem.ari
res.tandel.cri

##RKM
res.rkm.nmi = NMI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.ari = ARI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.cri = intCriteria(rkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.rkm.nmi
res.rkm.ari
res.rkm.cri


##FKM
res.fkm.nmi = NMI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.ari = ARI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.cri = intCriteria(fkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.fkm.nmi
res.fkm.ari
res.fkm.cri

```


# Yale
## IMPORT THE DATASET
```{r}
#CHANGE THE name of the file to USPC.mat
dataset<- readMat("data/Yale.mat")
#change $fea to poissbly X or x 
features<-dataset$X
#change $gnd to possibly y or Y  
labels<-as.vector(dataset$Y)
n_labels = length(unique(labels))
ndim= 2
dim(features)
```
## RUN cluspca wit different parameters
```{r}
tandem = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 1, seed = 1234,rotation = "varimax",nstart = 1)
RKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0.5, seed = 1234,rotation = "varimax")
FKM = cluspca(data = features,nclus = n_labels, ndim =  ndim, alpha = 0, seed = 1234,rotation = "varimax")

plot(tandem$ind$obscoord, col=labels)
plot(RKM$ind$obscoord, col=labels)
plot(FKM$ind$obscoord, col=labels)



#evaluating the clustering
##tandem
res.tandem.nmi = NMI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.ari = ARI(as.vector(tandem$cluster),as.vector(labels))
res.tandem.cri = intCriteria(tandem$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.tandem.nmi
res.tandem.ari
res.tandel.cri

##RKM
res.rkm.nmi = NMI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.ari = ARI(as.vector(RKM$cluster),as.vector(labels))
res.rkm.cri = intCriteria(rkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.rkm.nmi
res.rkm.ari
res.rkm.cri


##FKM
res.fkm.nmi = NMI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.ari = ARI(as.vector(FKM$cluster),as.vector(labels))
res.fkm.cri = intCriteria(fkm$obscoord,as.integer(true_labels),c("Silhouette","Davies_Bouldin"))
res.fkm.nmi
res.fkm.ari
res.fkm.cri

```
