---
title: "R Notebook"
output: html_notebook
---



```{r}
setwd("/Users/vanna/Documents/PPD/")
      
path=getwd()

```

```{r}
install.packages("clusterCrit")
install.packages(c("digest", "caTools", "bitops"))
```
```{r}
install.packages("png")
```

#1 IMPORTING LIBRARY

```{r}
library("png")
library("colorspace")         
library("raster")
library("EMMIXmfa")
library("aricode")
library("OpenImageR")
library("clusterCrit")
library("FactoMineR")
library("R.matlab")
```
#2 PREPARING DATA

```{r}
#Plotting of the images of the dataset
x<-readPNG("coil-20-proc/obj1__0.png")
print(dim(x))
image(x,
      col=gray.colors(10, start=0.3,end=1, gamma=2))
y<-resizeImage(x,64,64,method="nearest")
print(dim(y))
image(y,
      col=gray.colors(10, start=0.3,end=1, gamma=2))
```


```{r}

# We get all the names from the file that contains the images of coil20
namelist=list.files("/Users/vanna/Documents/PPD/coil-20-proc/" , pattern=NULL, all.files=FALSE,full.names=FALSE)
readPNG(namelist[1])
#Images are resize from 128*128 to 32*32
#l32 is a list containing 1440 matrix, each matrix represent an image
l32<-list()
for (i in 1:length(namelist))
  l32[[i]]<-resizeImage(readPNG(namelist[i]),32,32,method="nearest")
```

```{r}

print(dim(l32[[1]]))
m=as.vector(l32[[1]])

print(length(m))

```

```{r}
#In order to apply the mfa, we need to convert each matrix as a vector
data32<- matrix(nrow=1440,ncol = length(m))
for (i in 1:1440)
  data32[i,]<-as.vector(l[[i]])
```



```{r}
#We create a vector containing the true labels. Image of the dataset are already sorted
true_label<- c()
for (i in 1:20)
  for (j in 1:72)
  
    true_label<-append(true_label,i)
  
```


```{r}
#mfa on dataset with 2 dimensions
model<- mfa(data, 20, 2,  itmax = 2, nkmeans =2 , nrandom = 2,
tol = 1.e-5, sigma_type = 'common', D_type = 'common', init_clust = NULL,
init_para = NULL, conv_measure = 'diff', warn_messages = TRUE)
```

#3 CLUSTERING

```{r}
mfa_label<-model$clust
coil20_ARI_restult=ARI(true_label,mfa_label)
print(paste0("ARI: ", ARI_restult))
coil20_NMI_restult=NMI(true_label,mfa_label)
print(paste0("NMI: ", NMI_restult))
```

#4 SEPARABILITY


```{r}
#plotting the indivuals after MFA
plot(model$Umean,col=true_label)

```

```{r}
#plotting the individuals after PCA
pca_coil<-PCA(data32,ncp=2, axes=c(1,2))
plot(pca_coil$ind$coord, col=true_label)
```
```{r}
#PCA separabilité
intCriteria(pca_coil$ind$coord,true_label,c("Silhouette","Davies_Bouldin"))

```

```{r}
#MFA separabilité
intCriteria(model$Umean,true_label,c("Silhouette","Davies_Bouldin"))
```
#5 YALE


```{r}
setwd("/Users/vanna/Documents/PPD")
yale<-read.mat("/DATASET/Yale.mat")
```


```{r}
plot(model2$Umean)
intCriteria(model2$Umean,true_label,c("Silhouette","Davies_Bouldin"))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

